---
title: "ChapterTwo_ManuscriptCode"
output: html_document
date: "2023-04-08"
editor_options: 
  chunk_output_type: console
---


```{r}
setwd("/Users/whiteabalone/Desktop/Postdoc/gradschool/UVM/Copepods/ExperimentalData_UVM")

#install.packages("sos")
library(sos)
findFn("TukeyHSD")
```

Load in libraries
```{r}
library(tidyverse)
library(ggplot2)
library(ggpubr)
library(ggExtra)
library(rcompanion)
library(FSA)
library(car)
library(ARTool)
library(lme4)
library(reshape2)
library(grid)
library(gridExtra)
```

Loading in Upper Lethal Temperature Data
```{r}
mydata <- read.table("UCONN_ULT_Final.csv", header=TRUE, 
  	sep=",")
head(mydata)
```


Loading LLS Data
```{r}
myLLSdata <- read.table("UCONN_LLS_Reps_NoTreat.csv", header=TRUE, 
  	sep=",")
head(myLLSdata)
```


Loading Temp by Salinity data
```{r}
TSdata <- read.table("SalintyTemp.csv", header=TRUE, 
  	sep=",")
head(TSdata)
TSdata$Salinity <- as.factor(TSdata$Salinity)
```

First want to look at the normality of each dataset

Upper Lethal Temperature Data Normality
```{r}
ggqqplot(mydata$ULT)  #Not too far off
# Q-Q plot (or quantile-quantile plot) draws the correlation between a given sample 
# and the normal distribution. A 45-degree reference line is also plotted.

ggdensity(mydata$ULT, xlab = "ULT") 

shapiro.test(mydata$ULT)
```

Shapiro-Wilk normality test

data:  mydata$ULT
W = 0.93417, p-value = 0.0005199

Significant p value means different than normal distribution


Log Transforming Data
```{r}

mydata$LogULT <- log(mydata$ULT)
mydata

```


Looking to see if data is normally distributed

```{r}
ggqqplot(mydata$LogULT) 

ggdensity(mydata$LogULT, xlab = "LogULT") 

shapiro.test(mydata$LogULT)
```

Shapiro-Wilk normality test

data:  mydata$LogULT
W = 0.93827, p-value = 0.0008484


Square root transformation
```{r}

mydata$SquareULT <- sqrt(mydata$ULT)
mydata

```


Looking to see if data is normally distributed

```{r}
ggqqplot(mydata$SquareULT) 
# Q-Q plot (or quantile-quantile plot) draws the correlation between a given sample 
# and the normal distribution. A 45-degree reference line is also plotted.

ggdensity(mydata$SquareULT, xlab = "SquareULT") 

shapiro.test(mydata$SquareULT)
```

	Shapiro-Wilk normality test

data:  mydata$SquareULT
W = 0.93629, p-value = 0.0006685


Checking for homogeneity of variance
```{r}
head(mydata)
leveneTest(ULT~Group, data=mydata)
leveneTest(LogULT~Group, data=mydata)
leveneTest(SquareULT~Group, data=mydata)
```
All significantly different than homogeneous variance

Looking at anova to see how residuals look 
```{r}
Model_aov <- aov(ULT~Group, data = mydata)
summary(Model_aov)
plot(Model_aov)

```




LLS Data Normality
```{r}
ggqqplot(myLLSdata$OLLS)  #Not too far off
# Q-Q plot (or quantile-quantile plot) draws the correlation between a given sample 
# and the normal distribution. A 45-degree reference line is also plotted.

ggdensity(myLLSdata$OLLS, xlab = "LLS") 

shapiro.test(myLLSdata$OLLS)
```
Shapiro-Wilk normality test

data:  myLLSdata$OLLS
W = 0.84058, p-value = 2.538e-05

Not normal


Checking for homogeneity of variance
```{r}
head(myLLSdata)
leveneTest(OLLS~Group, data=myLLSdata)
```
Levene's Test for Homogeneity of Variance (center = median)
      Df F value Pr(>F)
group  2  0.7392 0.4837
      41  
      
Looks like there is homogeneous variance here 

Looking at anova to see how residuals look 
```{r}
Model_aov_LLS <- aov(OLLS~Group, data = myLLSdata)
summary(Model_aov_LLS)
plot(Model_aov_LLS)
```


Temp by Sal Data Normality
```{r}
ggqqplot(TSdata$ULT)  #Not too far off
# Q-Q plot (or quantile-quantile plot) draws the correlation between a given sample 
# and the normal distribution. A 45-degree reference line is also plotted.

ggdensity(TSdata$ULT, xlab = "ULT") 

shapiro.test(TSdata$ULT)
```
Shapiro-Wilk normality test

data:  TSdata$ULT
W = 0.88583, p-value = 0.0006497

Not normal


Checking for homogeneity of variance
```{r}
head(TSdata)
leveneTest(ULT~Salinity, data=TSdata)
```
Levene's Test for Homogeneity of Variance (center = median)
      Df F value Pr(>F)
group  2  0.7978 0.4577
      38    
      
Looks like there is homogeneous variance here

Looking at anova to see how residuals look 
```{r}
Model_aov_TS <- aov(ULT~Salinity, data = TSdata)
summary(Model_aov_TS)
plot(Model_aov_TS)
```


Want to make two subsets of the data ... one for looking at plasticity and one for looking at relaxed selection

Plasticity subset
```{r}
PlasticData <- mydata[ which(mydata$Group=='Control' ),]
PlasticData2 <- mydata[ which(mydata$Group=='Development' ),]
PlasticData3 <- mydata[ which(mydata$Group=='ThreeGens' ),]
PlasticData4 <- mydata[ which(mydata$Group=='>25Gens' ),]
PlasticData
PlasticData2
PlasticData3
PlasticData4
PlasticityData <- rbind(PlasticData, PlasticData2,PlasticData3,PlasticData4)
PlasticityData

```

Relaxed Selection Subset
```{r}

RelaxData2 <- mydata[ which(mydata$Group=='DevelopmentAmbient' ),]
RelaxData3 <- mydata[ which(mydata$Group=='ThreeGensAmbient' ),]
RelaxData4 <- mydata[ which(mydata$Group=='>25Gens' ),]
RelaxData5 <- mydata[ which(mydata$Group=='Control' ),]

RelaxData2
RelaxData3
RelaxData4
RSData <- rbind( RelaxData2,RelaxData3,RelaxData4,RelaxData5)
RSData

```

Subsetting LLS Data

```{r}
PlasticLLS <- myLLSdata[ which(myLLSdata$Group=='Control' ),]
PlasticLLS2 <- myLLSdata[ which(myLLSdata$Group=='Development' ),]
PlasticLLS3 <- myLLSdata[ which(myLLSdata$Group=='>25Gens' ),]
PlasticLLS
PlasticLLS2
PlasticLLS3
PlasticityLLS <- rbind(PlasticLLS, PlasticLLS2, PlasticLLS3)
PlasticityLLS
```


```{r}
myLLSdata
RelaxDataLLS2 <- myLLSdata[ which(myLLSdata$Group=='DevelopmentAmbient' ),]
RelaxDataLLS3 <- myLLSdata[ which(myLLSdata$Group=='>25Gens' ),]
RelaxDataLLS4 <- myLLSdata[ which(myLLSdata$Group=='Control' ),]

RelaxDataLLS2
RelaxDataLLS3
RelaxDataLLS4
RSDataLLS <- rbind( RelaxDataLLS2,RelaxDataLLS3,RelaxDataLLS4)
RSDataLLS
```


Determining whether or not replicate impacts ULT and LLS

Assessing effect of replicate for ULT
```{r}
UltKwRep <- kruskal.test(ULT~Replicate, mydata)
UltKwRep
```
	Kruskal-Wallis rank sum test

data:  ULT by Replicate
Kruskal-Wallis chi-squared = 4.1994, df = 3, p-value = 0.2407

Okay so not a significant effect of Replicate here ... what about for LLS


```{r}
LlsKwRep <- kruskal.test(OLLS~Replicate, data=PlasticityLLS)
LlsKwRep
```

	Kruskal-Wallis rank sum test

data:  OLLS by Replicate
Kruskal-Wallis chi-squared = 17.53, df = 3, p-value = 0.0005497

Significant effect of replicate for LLS


Boxplot of replicates for LLS

```{r}
#Want to add Kruskal Wallis results to the plot


str(PlasticityLLS)
PlasticityLLS$Group <- factor(PlasticityLLS$Group,
    levels = c(">50Gens","Development","Control"),ordered = TRUE)

TreatLabs <- c(">50Gens","Development","Control")
PlasticityLLS$Treatment<- as.factor(PlasticityLLS$Treatment)

PlasticityLLS$Replicate<- as.factor(PlasticityLLS$Replicate)

p <- ggplot(PlasticityLLS, aes(x=Replicate, y=OLLS, fill=Treatment)) + 
    geom_boxplot(aes(middle = mean(OLLS)), fatten = 5) + stat_boxplot(geom = "errorbar")

#Create a text


StatLabelLls <- grobTree(textGrob("Kruskal-Wallis chi-squared = 17.53, df = 3, p-value = 0.0005497", x="1",  y=12, hjust=0,
  gp=gpar(col="black", fontsize=13)))
# Plot

p  + scale_x_discrete(labels=c("Control" = "Ambient", "Development" = bquote(AM[DevA=OW]),">50Gens" = "OW")) + ylab("Lower Lethal Salinity (ppt)")+ annotate("text", x = 2.5, y=12, label = "Kruskal-Wallis chi2 = 17.53, df = 3, p-value = 0.0005497")

```

Boxplot of replicates for ULT

```{r}
mydata
str(mydata)
mydata$Group <- factor(mydata$Group,
    levels = c(">50Gens","Development","Control", "DevelopmentAmbient","ThreeGens","ThreeGensAmbient"),ordered = TRUE)

TreatLabs <- c(">50Gens","Development","Control", "DevelopmentAmbient","ThreeGens","ThreeGensAmbient")
mydata$Treatment<- as.factor(mydata$Treatment)

mydata$Replicate<- as.factor(mydata$Replicate)

p <- ggplot(mydata, aes(x=Replicate, y=ULT, fill=Treatment)) + 
    geom_boxplot(aes(middle = mean(ULT)), fatten = 5) + stat_boxplot(geom = "errorbar")

p  + scale_x_discrete(labels=c("Control" = "Ambient", "Development" = bquote(AM[DevA=OW]),">50Gens" = "OW")) + ylab("Upper Lethal Temperature (°C)")+ annotate("text", x = 2.5, y=39.5, label = "Kruskal-Wallis chi2 = 4.1994, df = 3, p-value = 0.2407")

```




Effect of Group on LLS
```{r}
kruskal.test(OLLS ~ Group, data=PlasticityLLS)
```

Use the ART ANOVA to incorporate both factors in the model
```{r}
PlasticityLLS$Group <- as.factor(PlasticityLLS$Group)
m2 <- art(OLLS ~ Group+ (1|Replicate), data=PlasticityLLS)
summary(m2)
```

Aligned Rank Transform of Factorial Model

Call:
art(formula = OLLS ~ Group + (1 | Replicate), data = PlasticityLLS)

Column sums of aligned responses (should all be ~0):
Group 
    0 

F values of ANOVAs on aligned responses not of interest (should all be ~0):
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 

```{r}
Model2 <- anova(m2)
summary(Model2)
Model2
```

Analysis of Variance of Aligned Rank Transformed Data

Table Type: Analysis of Deviance Table (Type III Wald F tests with Kenward-Roger df) 
Model: Mixed Effects (lmer)
Response: art(OLLS)

              F Df Df.res  Pr(>F)  
1 Group 0.66707  2 39.234 0.51893  
---
Signif. codes:   0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1 

With or without replicate... no effect of group on LLS

Assessing effect of group for ULT
```{r}
TreatMod <- kruskal.test(ULT~Group, mydata)
TreatMod
```
	Kruskal-Wallis rank sum test

data:  ULT by Group
Kruskal-Wallis chi-squared = 23.601, df = 5, p-value = 0.000259


```{r}
DT = dunnTest(ULT ~ Group,
              data=mydata,
              method="bh")
DT
```

                              Comparison          Z      P.unadj       P.adj
1                      >25Gens - Control  2.8468296 0.0044156995 0.016558873
2                  >25Gens - Development -0.8134565 0.4159563657 0.479949653
3                  Control - Development -3.6527756 0.0002594210 0.001945657
4           >25Gens - DevelopmentAmbient  1.1688398 0.2424681971 0.363702296
5           Control - DevelopmentAmbient -1.5918809 0.1114114656 0.185685776
6       Development - DevelopmentAmbient  1.9509833 0.0510590338 0.109412215
7                    >25Gens - ThreeGens -1.1419919 0.2534573764 0.345623695
8                    Control - ThreeGens -3.7841283 0.0001542482 0.002313723
9                Development - ThreeGens -0.3926278 0.6945944115 0.694594411
10        DevelopmentAmbient - ThreeGens -2.1922474 0.0283616457 0.070904114
11            >25Gens - ThreeGensAmbient  1.9455093 0.0517137076 0.096963202
12            Control - ThreeGensAmbient -0.8550675 0.3925138023 0.490642253
13        Development - ThreeGensAmbient  2.7386700 0.0061688259 0.018506478
14 DevelopmentAmbient - ThreeGensAmbient  0.7368135 0.4612358028 0.494181217
15          ThreeGens - ThreeGensAmbient  2.9290609 0.0033998783 0.016999391

Levene test on plasticity data
```{r}
str(PlasticityData)

PlasticityData$Group <- as.factor(PlasticityData$Group)

PlasticityData <- PlasticityData %>% group_by(Group) %>% 
  mutate(ULT.med = ifelse(ULT,median(ULT, na.rm=TRUE), ifelse(ULT=NA, NA)))
PlasticityData
```
The code above skips NA values and calculates sample medians for each factor combination, putting them in a new column (dat.med) in the dataset.

Then we calculate the residuals, changing them to absolute values and putting them in another column:

```{r}
PlasticityData$ULT.med.res<-abs(PlasticityData$ULT-PlasticityData$ULT.med)

# Then we run an ANOVA, and post-hoc if necessary:
levene.dat.aov<-aov(ULT.med.res~Group,PlasticityData)
#levene.dat.aov<-aov(ULT.med.res~Group+Error(Subject/(Group)),PlasticityData)
#the commented out code is for repeated measures anova ... which we don't need
summary(levene.dat.aov)
TukeyHSD(levene.dat.aov)
```

$Group
                              diff        lwr        upr     p adj
Control->25Gens       -0.116666667 -0.6513357  0.4180024 0.9377888
Development->25Gens    0.664583333  0.1684314  1.1607352 0.0044198
ThreeGens->25Gens      0.008333333 -0.5263357  0.5430024 0.9999742
Development-Control    0.781250000  0.2540592  1.3084408 0.0013992
ThreeGens-Control      0.125000000 -0.4385907  0.6885907 0.9349468
ThreeGens-Development -0.656250000 -1.1834408 -0.1290592 0.0091316

Testing significance of group on LLS

```{r}
kruskal.test(OLLS~Group, data=myLLSdata)
```

data:  OLLS by Group
Kruskal-Wallis chi-squared = 0.80578, df = 2, p-value = 0.6684

(Compared to 0.51893 with replicate in the model)

```{r}
kruskal.test(OLLS~Group, data=RSDataLLS)
```
data:  OLLS by Group
Kruskal-Wallis chi-squared = 0.20043, df = 1, p-value = 0.6544

```{r}
kruskal.test(OLLS~Group, data=PlasticityLLS)
```
	Kruskal-Wallis rank sum test

data:  OLLS by Group
Kruskal-Wallis chi-squared = 0.80578, df = 2, p-value = 0.6684

No matter which groups you look at ... no effect of temp on LLS

Temperature Salinity Analysis No Ham Beach

```{r}
TSdata$Population <- as.factor(TSdata$Population)

#Subset data for only esker point
TSdata

AmbientOnly <- subset(TSdata, Population == "UCONNControl")

m <- art(ULT ~ Salinity, data=AmbientOnly)
summary(m)
```

```{r}
art.con(m,"Salinity")
```
 contrast                estimate   SE df t.ratio p.value
 Salinity15 - Salinity20    -4.05 2.90 17  -1.398  0.3640
 Salinity15 - Salinity30    -6.90 2.90 17  -2.385  0.0708
 Salinity20 - Salinity30    -2.86 2.78 17  -1.027  0.5705




ART Anova for temperature salinity analysis
```{r}
TSdata$Population <- as.factor(TSdata$Population)
m <- art(ULT ~ Population*Salinity, data=TSdata)
summary(m)
```

Contrasts
```{r}
art.con(m,"Population")
```

 contrast          estimate   SE df t.ratio p.value
 HB - UCONNControl       18 2.58 35   6.995  <.0001

```{r}
art.con(m,"Salinity")
```
 contrast                estimate   SE df t.ratio p.value
 Salinity15 - Salinity20   -12.76 4.15 35  -3.072  0.0112
 Salinity15 - Salinity30   -14.19 4.15 35  -3.416  0.0045
 Salinity20 - Salinity30    -1.43 4.07 35  -0.351  0.9345

Plotting plasticity result
```{r}
#Turn your 'treatment' column into a character vector
PlasticityData$Group <- as.character(PlasticityData$Group)
#Then turn it back into a factor with the levels in the correct order
PlasticityData$Group <- factor(PlasticityData$Group, levels=unique(PlasticityData$Group))

PlasticityData$Group <- factor(PlasticityData$Group, levels=c("Control", "Development", "ThreeGens", ">25Gens"))

PlasticityData$Treatment<- as.factor(PlasticityData$Treatment)

p <- ggplot(PlasticityData, aes(x=Group, y=ULT, fill=Treatment)) + 
  geom_boxplot(aes(fatten = 5) + stat_boxplot() ) # Changing the middle line to the mean and widening the line

Plot1 <- p + geom_dotplot(binaxis='y', stackdir='center', dotsize=0.7)+ theme_classic()+ geom_text(aes(label=c("a"),y=37.5,x="Control"),size=10)+ geom_text(aes(label=c("b"),y=39.5,x="Development"),size=10)+ geom_text(aes(label=c("b"),y=38,x="ThreeGens"),size=10)+ geom_text(aes(label=c("b"),y=38,x=">25Gens"),size=10)+ theme(text = element_text(size = 18))+ ylab("Upper Lethal Temperature (°C)") + xlab(" ")+ scale_x_discrete(labels=c("Control" = "AM", "Development" = bquote(AM[DevOW]),"ThreeGens" = bquote(AM["3GensOW"]),">25Gens" = "OW"))
Plot1 +scale_fill_manual(values = c("dodgerblue","red3"))
```

Plotting Relaxed Selection Result

```{r}
RSData
RSData$Group <- factor(RSData$Group,
    levels = c(">25Gens","DevelopmentAmbient","ThreeGensAmbient","Control"),ordered = TRUE)

TreatLabs <- c(">25Gens","DevelopmentAmbient","ThreeGensAmbient", "Control")
RSData$Treatment<- as.factor(RSData$Treatment)
p <- ggplot(RSData, aes(x=Group, y=ULT, fill=Treatment)) + 
    geom_boxplot() + stat_boxplot()

p  + scale_x_discrete(labels=c("Control" = "Ambient", "DevelopmentAmbient" = bquote(OW[DevAM]),"ThreeGensAmbient" = bquote(OW["3GensAM"]),">25Gens" = "OW"))




RSPLOT <- p + geom_dotplot(binaxis='y', stackdir='center', dotsize=0.7)+ theme_classic()+geom_text(aes(label=c("a"),y=37.5,x=">25Gens"),size=10)+ geom_text(aes(label=c("a,b"),y=36.8,x="DevelopmentAmbient"),size=10)+geom_text(aes(label=c("a,b"),y=36.8,x="ThreeGensAmbient"),size=10)+geom_text(aes(label=c("b"),y=36.8,x="Control"),size=10)+ theme(text = element_text(size = 18)) + ylab("Upper Lethal Temperature (°C)") + xlab(" ") + scale_x_discrete(labels=c("Control" = "AM", "DevelopmentAmbient" = bquote(OW[DevAM]),"ThreeGensAmbient" = bquote(OW["3GensAM"]),">25Gens" = "OW")) 

RSPLOT+ scale_fill_manual(values=c("dodgerblue","red3"))
```

LLS Plot
```{r}
#Turn your 'treatment' column into a character vector
PlasticityLLS$Group <- as.character(PlasticityLLS$Group)
#Then turn it back into a factor with the levels in the correct order
PlasticityLLS$Group <- factor(PlasticityLLS$Group, levels=unique(PlasticityLLS$Group))

PlasticityLLS$Group <- factor(PlasticityLLS$Group, levels=c("Control", "Development",  ">25Gens"))

PlasticityLLS$Treatment<- as.factor(PlasticityLLS$Treatment)
p <- ggplot(PlasticityLLS, aes(x=Group, y=OLLS, fill=Treatment)) + 
    geom_boxplot(aes() + stat_boxplot())
p


p + geom_dotplot(binaxis='y', stackdir='center', dotsize=0.7)+ theme_classic()+ scale_fill_manual(values=c("dodgerblue","red3"))+ylab("Lower Lethal Salinity (ppt)") + scale_x_discrete(labels=c("Control" = "AM", "Development" = bquote(AM[DevOW]),">25Gens" = "OW"))+ xlab(" ")+ geom_text(aes(label=c("a"),y=18,x="Control"),size=10)+geom_text(aes(label=c("a"),y=18,x="Development"),size=10)+geom_text(aes(label=c("a"),y=18,x=">25Gens"),size=10)+ theme(text = element_text(size = 22)) 
```


Difference in means between treatments?
```{r}
PlasticityLLS

PlasticityLLS %>%
  group_by(Group) %>%
  summarise_at(vars(OLLS), list(name = mean))
```

Temp by salinity plots
```{r}
mydata_melt <- melt(TSdata)
mydata_melt

mydata_melt$Salinity <- factor(mydata_melt$Salinity,
    levels = c("30","20","15"),ordered = TRUE)
```

```{r}
 TreatLabs <- c("30","20","15")
```

```{r}

plot1 <- ggplot(mydata_melt,aes(x=Salinity,y=value,fill=Population))+  geom_boxplot(aes(middle = mean(value)), fatten = 5) + stat_boxplot(geom = "errorbar")

plot2 <- (plot1 + geom_dotplot(binaxis='y', stackdir='center',dotsize=0.5,
                 position=position_dodge(.7))+scale_fill_manual(values=c("grey3","grey3") ))
plot2

plot2 +ylab("Upper Lethal Temperature (°C)")+ xlab("Salinity (ppt)")  + scale_x_discrete(labels= TreatLabs) +scale_fill_discrete(name = "Population", labels = c("Hammonasset Beach", "Esker Point"))+ scale_fill_manual(values=c("purple4","darkorange3"),name = "Population", labels = c("Hammonasset Beach", "(Ambient) Esker Point") ) + annotate("text", x = "30", hjust=4.8, y = 39,label = "a", size=7) + 
  annotate("text", x = "30", hjust=-4.8 ,y = 37, label = "b", size=7) + annotate("text", x = "20", hjust=4.8, y = 39,label = "a", size=7)  + annotate("text", x = "20", hjust=-4.8 ,y = 37, label = "b", size=7) + annotate("text", x = "15", hjust=4.8, y = 39,label = "c", size=7)  + annotate("text", x = "15", hjust=-4.8 ,y = 37, label = "d", size=7)+ theme_classic(base_size = 22)

```

TS Plots ambient only

```{r}
mydata_meltSal <- melt(AmbientOnly)
mydata_meltSal

mydata_meltSal$Salinity <- factor(mydata_meltSal$Salinity,
    levels = c("30","20","15"),ordered = TRUE)
```

```{r}
 TreatLabs <- c("30","20","15")
```

```{r}

plot1 <- ggplot(mydata_meltSal,aes(x=Salinity,y=value,fill=Population))+  geom_boxplot(aes() + stat_boxplot())

plot2 <- (plot1 + geom_dotplot(binaxis='y', stackdir='center',dotsize=0.7,
                 position=position_dodge(.7))+scale_fill_manual(values=c("grey3") ))
plot2

plot2 +theme_classic(base_size = 22)+ylab("Upper Lethal Temperature (°C)")+ xlab("Salinity (ppt)")  + scale_x_discrete(labels= TreatLabs) +scale_fill_discrete(name = "Population", labels = c("Hammonasset Beach", "Esker Point"))+ scale_fill_manual(values=c("dodgerblue"),name = "Population", labels = c("Ambient")+ theme(text = element_text(size = 50))  ) + geom_text(aes(label=c("a"),y=37,x="30"),size=10)+geom_text(aes(label=c("a"),y=37,x="20"),size=10)+geom_text(aes(label=c("a"),y=37,x="15"),size=10)+ theme(text = element_text(size = 22)) 

# annotate("text", x = "30", hjust=4.8, y = 39,label = "a", size=7) + 
#   annotate("text", x = "30", hjust=-4.8 ,y = 37, label = "b", size=7) + annotate("text", x = "20", hjust=4.8, y = 39,label = "a", size=7)  + annotate("text", x = "20", hjust=-4.8 ,y = 37, label = "b", size=7) + annotate("text", x = "15", hjust=4.8, y = 39,label = "c", size=7)  + annotate("text", x = "15", hjust=-4.8 ,y = 37, label = "d", size=7)+ theme_classic(base_size = 22)

```



















What is the loss of ULT across salinity treatments for AM line?

```{r}

#subset for UCONNControl animals

AmLLSData <- mydata_meltSal[ which(mydata_meltSal$Population=='UCONNControl' ),]

AmLLSData %>%
  group_by(Salinity) %>%
  summarise_at(vars(value), list(name = mean))

```

Levene test comparing variance between populations

```{r}
str(mydata_melt)

mydata_melt$Population <- as.factor(mydata_melt$Population)

mydata_melt <- mydata_melt %>% group_by(Population) %>% 
  mutate(value.med = ifelse(value,median(value, na.rm=TRUE), ifelse(value=NA, NA)))
mydata_melt
```
The code above skips NA values and calculates sample medians for each factor combination, putting them in a new column (dat.med) in the dataset.

Then we calculate the residuals, changing them to absolute values and putting them in another column:

```{r}
mydata_melt$value.med.res<-abs(mydata_melt$value-mydata_melt$value.med)
mydata_melt
# Then we run an ANOVA, and post-hoc if necessary:
levene.dat.aov<-aov(value.med.res~Population,mydata_melt)
#levene.dat.aov<-aov(ULT.med.res~Group+Error(Subject/(Group)),PlasticityData)
#the commented out code is for repeated measures anova ... which we don't need
summary(levene.dat.aov)
TukeyHSD(levene.dat.aov)
```

$Population
                      diff        lwr         upr     p adj
UCONNControl-HB -0.4333333 -0.8046929 -0.06197382 0.0233597



Appendix Figure Two


Loading in ULT Data
```{r}

mydata <- read.table("LHS_ctmax_Complete.csv", header=TRUE, 
  	sep=",")
head(mydata)
```

```{r}
mysubdata <- within(mydata, rm(Plate))
mysubsubdata <- within(mysubdata, rm(Sex))
mysubsubdata

mysubsetdata <- within(mysubsubdata, rm(MeanMax))
mysubsetdata
```

```{r}

mydata_melt <- melt(mysubsetdata)
mydata_melt
```


```{r}

 NYdata<- mydata_melt %>% filter(Population == "NewYork")
 
 NYdata
 
 NYdatadata <-  NYdata %>% filter(Stage == "Adult")
 
 NYdatadata
 
NYplot <- ggplot(NYdatadata, aes(x=Population, y=value)) + 
  geom_boxplot()+ylab("Upper Lethal Temperature (°C)") 

NYplot

nNYplot <- NYplot + geom_dotplot(binaxis='y', stackdir='center',dotsize=0.75,position=position_dodge(.5))
nNYplot + theme_classic(base_size = 22)
```


Appendix Figure Three


```{r}
mydata <- read.table("UCONN_GradualSalinity_Trial.csv", header=TRUE, 
  	sep=",")
head(mydata)
```


reformat
```{r}
mydata$Treatment <- paste(mydata$Line,mydata$Condition)
mydata
```

Subset the data to remove the extra columns
```{r}

mysubdata <- within(mydata, rm(Line))
mysubsubdata <- within(mysubdata, rm(Condition))
plotdata <- within(mysubsubdata,rm(Replicate))

plotdata

```




```{r}
mydata_melt <- melt(plotdata)
mydata_melt
```


```{r}
plot1 <- (ggplot(mydata_melt,aes(x=Sex,y=value,fill=Sex))+geom_boxplot(width=0.9/length(unique(mydata_melt$Sex)),position=position_dodge(.5)))

plot2 <- (plot1 + geom_dotplot(binaxis='y', stackdir='center', dotsize=0.75,
                 position=position_dodge(.5))+scale_fill_manual(values=c("grey3","grey3") ))
plot2

plot2 + scale_fill_manual(values=c("tomato","dodgerblue")) +ylab("Lower Lethal Salinity (ppt)") + theme_bw(base_size = 15)+guides(fill=guide_legend(
                 keywidth=0.4,
                 keyheight=0.4,
                 default.unit="inch")) + scale_y_continuous(breaks=c(0,2,4,6,8,10,12))

```














